\section{Presentations}

\subsection{Contributed Talks}
\orderedouterlist{
    \entry{
        Active Learning for Conditional Generative Compressed Sensing \href{https://drive.google.com/file/d/17TmlxLnCDfKFffg2FstlyZhrghPBcLdv/view?usp=sharing}{[pdf]}\\
        April 2026. ACC Meeting of the Minds, Tallahassee, FL.
    }

    \entry{
        Optimal Linear Baseline Models for Scientific Machine Learning \href{https://drive.google.com/file/d/1xQNVJsoN_FEYqPtXUWbEkxqTtOZz-ULf/view?usp=sharing}{[pdf]}\\
        January 2026. Joint Mathematics Meetings, AMS Contributed Paper Session on Computer Science, Information, and Communication, Washington, DC.
    }

    \entry{
        Optimal Linear Baseline Models for Scientific Machine Learning \href{https://drive.google.com/file/d/16ESkkK_1GZJbSuV3RSsXS3FGsBdfz1VB/view?usp=sharing}{[pdf]}\\
        November 2025. SIAM Student Chapter, Florida State University, Tallahassee, FL.
    }
}

\subsection{Poster Presentations}
\orderedouterlist{
    \entry{
        Active Learning for Conditional Generative Compressed Sensing \href{https://drive.google.com/file/d/1OmUsoYH13XJMJGRbqjIlHm4_BTZ9mZcR/view?usp=sharing}{[pdf]}\\
        April 2026. 26th Annual Undergraduate Research Symposium, Florida State University, Tallahassee, FL.
    }

    \entry{
        Optimal Rank-Constrained Mappings for Linear ED Architectures \href{https://drive.google.com/file/d/1oeuLd2K0Vo1pE5CPJJ_2nPsJamtbjpDO/view?usp=sharing}{[pdf]}\\
        March 2026. Florida Undergraduate Research Conference, University of North Florida, Jacksonville, FL.
    }

    \entry{
        Optimal Rank-Constrained Mappings for Linear ED Architectures \href{https://drive.google.com/file/d/1SIseeRLDQPWWQKgIVbE8S4KvZdyr00MK/view?usp=drive_link}{[pdf]}\\
        January 2026. Joint Mathematics Meetings AMS-PME Student Poster Session, Emory University, Atlanta, GA.
    }

    \entry{
        Optimal Rank-Constrained Mappings for Linear ED Architectures \href{https://drive.google.com/file/d/1SIseeRLDQPWWQKgIVbE8S4KvZdyr00MK/view?usp=drive_link}{[pdf]}\\
        August 2025. CMDS REU Poster Presentation, Emory University, Atlanta, GA.
    }

    \entry{
        Data-Driven Patient Allocation Optimization with Epidemic and Vaccine Modeling \href{https://drive.google.com/file/d/1SIseeRLDQPWWQKgIVbE8S4KvZdyr00MK/view?usp=sharing}{[pdf]}\\
        April 2025. 25th Annual Undergraduate Research Symposium, Florida State University, Tallahassee, FL.
    }

    \entry{
        Data-Driven Patient Allocation Optimization with Epidemic and Vaccine Modeling \href{https://drive.google.com/file/d/1LrSnga5b3sIamr5tF-Y2syaltmGvHuwD/view?usp=drive_link}{[pdf]}\\
        February 2025. Florida Undergraduate Research Conference, University of South Florida, Tampa, FL.
    }

    \entry{
        Learning Feasible States with ma-QAOA and QAOA for Constrained Optimization \href{https://drive.google.com/file/d/1HxUtPugzXacb4wPU3YHHVBDaIi-e3ZQ1/view?usp=drive_link}{[pdf]}\\
        January 2025. Joint Mathematics Meetings AMS-PME Student Poster Session, Seattle, WA.
    }

    \entry{
        Learning Feasible States with ma-QAOA and QAOA for Constrained Optimization \href{https://drive.google.com/file/d/1HxUtPugzXacb4wPU3YHHVBDaIi-e3ZQ1/view?usp=drive_link}{[pdf]}\\
        July 2024. UTK Summer Research Symposium, University of Tennessee, Knoxville, TN.
    }

    \entry{
        Cost-Effective Location Allocation for COVID-19 Patient Assignment in Florida: A Data-Driven Approach \href{https://drive.google.com/file/d/1VOaCZg7goQ2h4m-0AfPnLVREi_PvYpfh/view?usp=drive_link}{[pdf]}\\
        April 2024. 24th Annual Undergraduate Research Symposium, Florida State University, Tallahassee, FL.
    }

}
